Morphometric geometric demo: a between group analysis

### 2020-09-25 inst/gitbook/03_specific-tutorials.Rmd
Updated book

## But we can still plot both spaces by using the default plot functions
par(mfrow = c(1,2))
## Default plotting
plot(cust_subsets)
## Plotting with more arguments
plot(time_subsets, dimensions = c(4,5),
     main = "Some \"low\" dimensions")
```

@@

## Plotting the results
plot(dispRity_dtt, fig.width=8, fig.height=8)
```

>>>>

## But we can still plot both spaces by using the default plot functions
par(mfrow = c(1,2))
## Default plotting
plot(cust_subsets)
## Plotting with more arguments
plot(time_subsets, specific.args = list(dimensions = c(1,2)),
     main = "Some \"low\" dimensions")
```

@@

## Plotting the results
plot(dispRity_dtt)
```

### 2020-09-25 inst/gitbook/09_gmm-demo.Rmd
Updated book

# Palaeobiology demo: disparity-through-time and within groups

@@

```{r}
## Defining a the procrustes variance metric
## (as in geomorph::morphol.disparity)
proc.var <- function(matrix) {sum(matrix^2)/nrow(matrix)}
## The size metric
test_size <- test.metric(morphospace, metric = proc.var,
                         shifts = c("random", "size"))
plot(test_size)
summary(test_size)

>>>>

# Morphometric geometric demo: a between group analysis

@@

```{r, fig.width = 8, fig.height = 16}
## Defining a the procrustes variance metric
## (as in geomorph::morphol.disparity)
proc.var <- function(matrix) {sum(matrix^2)/nrow(matrix)}
## The size metric
test_size <- test.metric(morphospace, metric = proc.var,
                         shifts = c("random", "size"))
plot(test_size)
summary(test_size)
